Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-08 Papers/ms.tex
Huppenkothen reference updated
A bit more talking

{\revisions As with the `easy' dataset,
we generated 5,000 samples from the DNS target distribution and thinned
by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
performed, taking approximately 60 hours. The slower runtime in this case
was because $N_{\rm lens} = 10$, more CPU time was spent exploring parts of
the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
equally-weighted posterior samples.
}

@@

@@

@@

\bibitem[\protect\citeauthoryear{Huppenkothen et 
al.}{2015}]{magnetron} Huppenkothen D., et al., 2015,
accepted for publication in ApJ. arXiv:1501.05251

>>>>

@@

{\revisions As with the `easy' dataset,
we generated 5,000 samples from the DNS target distribution and thinned
by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
performed, taking approximately 60 hours. The slower runtime in this case
was because $N_{\rm lens} = 10$, more CPU time was spent exploring parts of
the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
equally-weighted posterior samples. The posterior distribution for the SIE
mass and the total substructure mass is given in Figure~\ref{fig:masses2}.
}

@@

{\revisions
To demonstrate the claim that we can infer something about the mass function
of substructures directly, we have plotted the posterior
distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
masses, in Figure~\ref{fig:mu_lens}.
}

@@

\bibitem[\protect\citeauthoryear{Huppenkothen et 
al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, ApJ, 810, 
66
